---
title: "GLOBAL TERRORISM EDA - Fathima Sadique"
output: flexdashboard::flex_dashboard
---

Frequent Years
===================================== 
Column 
-------------------------------------
    
### **Number of attacks from 1970 to 2017**
    
```{r}
library(flexdashboard)
library(rgeos)
library(readxl)
library(ggplot2)
library(dplyr)
library(ggpubr)
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library("data.table")
setwd("C:/Users/91886/Desktop/internship/TSF")
task_data<-read_excel("Terrorism.xlsx")

ggdensity(task_data, x = "iyear", xlab='Years', ylab='Density', 
          fill = "#6C93B4FF", color = "#6C93B4FF", rug = TRUE)
```
   
Column
-------------------------------------
   
### **Closer look at the number of attacks after 2010**

```{r}
years<-subset(task_data, task_data$iyear>=2010)
years_tab<-table(years$iyear)
years_df<-as.data.frame(years_tab)
years_df %>%
  ggplot(aes(x=Var1, y=Freq, fill=Freq))+
  geom_col() + xlab("Years") + ylab("Count") + labs(fill = "Count")

```   
 
Frequent Regions
=====================================

Column {data-width=650}
-------------------------------------
    
### **Number of attacks spread over the regions**
    
```{r, fig.width=10, fig.height=7}
Regions_tab<-table(task_data$region_txt)
Regions<-as.data.frame(Regions_tab)
ggplot(data=Regions, aes(x=Var1, y=Freq)) +
  geom_bar(stat="identity",fill="snow1") + coord_flip() + theme(panel.background = element_rect(fill = "#BFD5E3", colour = "#6D9EC1",size = 2, linetype = "solid")) + xlab("Regions") + ylab("Frequency")
```

Column {data-width=350, .tabset}
-------------------------------------
   
### **Areas affected in the Middle East and North Africa**

```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")
MiddEast<-subset(task_data,task_data$region_txt=='Middle East & North Africa')
ggplot(data = world) +
  geom_sf() +
  geom_point(data = MiddEast, aes(x = longitude, y = latitude), na.rm=T,size = 1, 
             shape = 23, fill = "indianred3", color="indianred4") + coord_sf(xlim = c(-20, 80), ylim = c(-40, 55), expand = FALSE) + theme(panel.background = element_rect(fill = "#BFD5E3", colour = "#6D9EC1",size = 2, linetype = "solid"))

```  

### **Areas affected in South Asia**

```{r}
SouthAsia<-subset(task_data,task_data$region_txt=='South Asia')
ggplot(data = world) +
  geom_sf() +
  geom_point(data = SouthAsia, aes(x = longitude, y = latitude), na.rm=T,size = 1, 
             shape = 23, fill = "indianred3", color="indianred4") + coord_sf(xlim = c(50, 120), ylim = c(0, 50), expand = FALSE) + theme(panel.background = element_rect(fill = "#BFD5E3", colour = "#6D9EC1",size = 2, linetype = "solid"))
```

### **Areas affected in South America**

```{r}
SouthAmerica<-subset(task_data,task_data$region_txt=='South America')
ggplot(data = world) +
  geom_sf() +
  geom_point(data = SouthAmerica, aes(x = longitude, y = latitude), na.rm=T,size = 1, 
             shape = 23, fill = "indianred3", color="indianred4") + coord_sf(xlim = c(-100, 0), ylim = c(-65, 20), expand = FALSE) + theme(panel.background = element_rect(fill = "#BFD5E3", colour = "#6D9EC1",size = 2, linetype = "solid"))
```


Hotspot Countries {data-orientation=rows}
=====================================

Row {data-width=80}
--------------------------------------

### Total attacks in Iraq
```{r}
c1=task_data %>% filter(country_txt=="Iraq") %>% nrow()
valueBox(value = c1, color = "coral")
```

### Total attacks in Pakistan
```{r}
c2=task_data %>% filter(country_txt=="Pakistan") %>% nrow()
valueBox(value = c2, color = "darksalmon")
```

### Total attacks in Afghanistan
```{r}
c3=task_data %>% filter(country_txt=="Afghanistan") %>% nrow()
valueBox(value = c3, color = "darkseagreen")
```

Row
----------------------------------

### **Top 5 affected countries**
```{r}
task_data$country_txt=as.factor(task_data$country_txt)
Countries_tab<-table(task_data$country_txt)
Countries<-as.data.frame(Countries_tab)
Countries <- Countries[order(Countries$Freq,decreasing = TRUE),]
top5<- Countries[1:5,]
names(top5)[names(top5) == "Var1"] <- "Countries"
names(top5)[names(top5) == "Freq"] <- "Number of attacks"
setDT(top5) 
top5 = top5[order(top5$`Number of attacks`),]
dotchart(top5$`Number of attacks`, labels = top5$`Countries`, col = c("skyblue","skyblue1","skyblue2","skyblue3","skyblue4"),
         cex = 1.0,pch=19, xlab = "Number of terrorist attacks")

```

### **Affected provinces of the top 3 countries**
```{r, fig.height=7}
Iraq<-subset(task_data,task_data$country_txt=='Iraq')
Pak<-subset(task_data,task_data$country_txt=='Pakistan')
Afg<-subset(task_data,task_data$country_txt=='Afghanistan')

Iraq_tab<-table(Iraq$provstate)
Iraq_prov<-as.data.frame(Iraq_tab)
Iraq_prov <- Iraq_prov[order(Iraq_prov$Freq,decreasing = TRUE),]
Iraq_5 <- Iraq_prov[1:5,]
Iraq_5$Country<-"Iraq"

Pak_tab<-table(Pak$provstate)
Pak_prov<-as.data.frame(Pak_tab)
Pak_prov$Country<-"Pakistan"
Pak_prov <- Pak_prov[order(Pak_prov$Freq,decreasing = TRUE),]
Pak_5 <- Pak_prov[1:5,]

Afg_tab<-table(Afg$provstate)
Afg_prov<-as.data.frame(Afg_tab)
Afg_prov$Country<-"Afghanistan"
Afg_prov <- Afg_prov[order(Afg_prov$Freq,decreasing = TRUE),]
Afg_5 <- Afg_prov[1:5,]

prov_tab<-rbind(Iraq_5,Pak_5,Afg_5)
prov_tab$Country<-as.factor(prov_tab$Country)

grps <- prov_tab$Country
my_cols <- c("turquoise4", "aquamarine4", "paleturquoise4")
dotchart(prov_tab$Freq, 
         groups = grps, gcolor = my_cols, ,
         color = my_cols[grps], labels=prov_tab$Var1,
         cex = 1.15,  pch = 19, xlab = "No. of attacks")
```

Mode of Attack {data-orientation=rows}
=====================================

Row {data-width=80}
--------------------------------------

### **BOMBING SUCCESS RATE**

```{r}
succ<-with(task_data, table(attacktype1_txt, success))
success_df<-data.frame("Success"=succ[,2],"Failure"=succ[,1])
success_df$Percent_Of_Success<-round((success_df$Success/(success_df$Success+success_df$Failure))*100)
success_df$tot=success_df$Success+success_df$Failure
success_df<-success_df[order(success_df$tot,decreasing=T),]

rate1 <-success_df[1,3]
gauge(rate1, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(0, 39), warning = c(40, 79), danger = c(80,100)
))
```

### **ARMED ASSAULT SUCCESS RATE**
```{r}
rate2 <-success_df[2,3]
gauge(rate2, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(0, 39), warning = c(40, 79), danger = c(80, 100)
))
```

### **ASSASSINATION SUCCESS RATE**
```{r}
rate3 <-success_df[3,3]
gauge(rate3, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(0, 39), warning = c(40, 79), danger = c(80, 100)
))
```

Row 
--------------------------------------

### **Frequency of each attack mode grouped by success and failure** 
``` {r, fig.width=15}
task_data$attacktype1_txt=as.factor(task_data$attacktype1_txt)
bar1=ggplot(data=task_data, mapping=aes(x=attacktype1_txt, fill=as.factor(success)))
bar1+geom_bar(width=0.4) + coord_flip() + scale_fill_manual(values=c("seashell", "thistle4"))+ theme(panel.background = element_rect(fill = "gray16", colour = "#6D9EC1",size = 2, linetype = "solid")) + xlab("Mode of Attack") + ylab("Total no. of attacks") + labs(fill = "Success - 1 / Failure - 0")
```

Targeted Categories 
=====================================

Column 
-------------------------------------
    
### **Spread of the 3 most common attacks from 1970 to 2017**
    
```{r}
attack_freq<-table(task_data$attacktype1_txt)
attack_freq<-as.data.frame(attack_freq)
attack_freq<-attack_freq[order(attack_freq$Freq,decreasing = TRUE),]
topattack_sub<-subset(task_data,task_data$attacktype1_txt=="Bombing/Explosion"|task_data$attacktype1_txt=="Armed Assault"|task_data$attacktype1_txt=="Assassination")
topattack_sub$attacktype1_txt<-factor(topattack_sub$attacktype1_txt)
ggplot(data=topattack_sub, mapping=aes(x=iyear, fill=as.factor(attacktype1_txt)))+geom_density(alpha=0.5) + theme(panel.background = element_rect(fill = "azure2", colour = "#6D9EC1",size = 2, linetype = "solid")) + xlab("Years") + ylab("Density") + labs(fill = "Mode of attack")
```
   
Column {.tabset}
-------------------------------------
   
### **The targeted categories** 

```{r, fig.height=7}
target_tab<-table(task_data$targtype1_txt)
target_type<-as.data.frame(target_tab)
dotchart(target_type$Freq, labels = target_type$Var1,
         cex = 1.0, xlab='No. of attacks', pch = 19, col = c("darkblue","dodgerblue"),
         cex.main = 2, cex.lab = 1.5)
```   
 
### **Weapons used under different circumstances**
    
```{r}
task_data$Classification <- ifelse(task_data$targtype1_txt == 'Utilities' | task_data$targtype1_txt == 'Transportation' | task_data$targtype1_txt == 'Tourists' | task_data$targtype1_txt == 'Religious Figures/Institutions' | task_data$targtype1_txt == 'Educational Institution' | task_data$targtype1_txt == 'Airports & Aircraft' | task_data$targtype1_txt == 'Telecommunication' | task_data$targtype1_txt == 'Private Citizens & Property' | task_data$targtype1_txt == 'NGO' | task_data$targtype1_txt == 'Business', 'Public',
                  ifelse(task_data$targtype1_txt == 'Violent Political Party' | task_data$targtype1_txt == 'Terrorists/Non-State Militia' | task_data$targtype1_txt == 'Police' | task_data$targtype1_txt == 'Military' | task_data$targtype1_txt == 'Maritime' | task_data$targtype1_txt == 'Journalists & Media' | task_data$targtype1_txt == 'Government (General)' | task_data$targtype1_txt == 'Government (Diplomatic)' | task_data$targtype1_txt == 'Food or Water Supply', 'Political', 'Other'))

task_data$weaptype1_txt[task_data$weaptype1_txt == 'Vehicle (not to include vehicle-borne explosives, i.e., car or truck bombs)'] <- 'Vehicular'
task_data %>% ggplot(aes(x = weaptype1_txt, fill=Classification)) + geom_bar(position='dodge',width=0.6) + scale_fill_manual(values=c("lightblue3", "lightcoral","lightblue4"))+coord_flip() +  theme(panel.background = element_rect(fill = "grey90", colour = "grey69",size = 2, linetype = "solid")) + xlab("Type of Weapon") + ylab("No. of attacks") + labs(fill = "Classification")
```